---
title: "AC_Dec_06"
author: "Srijan Kundu"
date: "2022-12-06"
output: pdf_document
---

Fit an Exponential distribution to the following data:

| Waiting time to failure | No. of Bulbs |
|-------------------------|--------------|
| 0-10                    | 56           |
| 10-20                   | 19           |
| 20-30                   | 14           |
| 30-40                   | 8            |
| 40-50                   | 4            |
| 50 and more             | 1            |

$E(x) = \lambda,\;\;\hat{\lambda} = \frac {1} {\bar{x}}.$

------------------------------------------------------------------------

```{r}
library(pracma)
library(matlib)
library(ggplot2)
library(ggpubr)
```



```{r}
class_int <- seq(0, 60, 10)
class <- c("0-10", "10-20", "20-30", "30-40", "40-50", "> 50")
x <- seq(5, 55, 10)
f <- c(56, 19, 14, 8, 4, 1)
```

```{r}
x_bar <- dot(f, x)/sum(f)
x_bar
l_hat <- 1/x_bar
l_hat
```

```{r}
st_var <- sum(((x - x_bar)**2)*f)/(sum(f) - 1)
st_var
st_dev <- sqrt(st_var)
```

Here, $E(x) = 14.02$.
We will fit an exponential distribution with parameter $\lambda = \frac{1}{14.02}$.

```{r}
p <- c(pexp(10, l_hat) - pexp(0, l_hat),
       pexp(20, l_hat) - pexp(10, l_hat),
       pexp(30, l_hat) - pexp(20, l_hat),
       pexp(40, l_hat) - pexp(30, l_hat),
       pexp(50, l_hat) - pexp(40, l_hat),
       pexp(Inf, l_hat) - pexp(50, l_hat))

p
```
Expected frequency:
```{r}
exp_freq <- p*sum(f)
exp_freq
```

Goodness of fit:
```{r}
df <- data.frame(class, f, exp_freq, p)
colnames(df) <- c("Class_Intervals", "Observed_Frequency", "Expected_Frequency", "Probability")
df
```

```{r}
#Chi-square test statistic
#df = (k-1-r) = (6-1-1) = 4; k = no. of obs, r = no. of parameters
chi <- (f - exp_freq)**2/exp_freq
sum(chi)
```
```{r}
qchisq(0.95, 4)
```
Here, $4.28 < 9.48$, so we accept $H_0$ that the fit with $Exp(0.7132)$ is good.

To compare the expected and observed frequencies for each class intervals, we use the following bar diagrams and the line diagrams:
```{r}
gg_obj <- ggplot(NULL, aes())
```

