---
title: "SD - Aug 30"
author: "Srijan Kundu"
date: "2022-08-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question: Draw 50 random sample of size 25 each from the following distributions:

### (i) Rectangular(0, 1)

### (ii) Normal(0, 1)

### (iii) Cauchy(0, 1)

## Compute the statistics below for each sample:

### (i) $\bar{X_n}$, (ii) $X_{(1)}$, (iii) $X_{(n)}$, (iv) $Med(X)$


```{r}
set.seed(30)
library(ggplot2)
```

## The Rectangular (0, 1) distribution:
### Drawing 50 random samples:

```{r}
samp1 <- replicate(50, runif(25, 0, 1))
samp1
```
### Calculating mean for the above sample:

```{r}
samp1_mean <- replicate(50, mean(runif(25, 0, 1)))
samp1_mean
```
### Calculating minimum for each of the above samples:

```{r}
samp1_min <- replicate(50, min(runif(25, 0, 1)))
samp1_min
```

### Calculating maximum for each of the above samples:

```{r}
samp1_max <- replicate(50, max(runif(25, 0, 1)))
samp1_max
```

### Calculating median for each of the above samples:

```{r}
samp1_mid <- replicate(50, median(runif(25, 0, 1)))
samp1_mid
```

### Plotting these 4 statistics:

```{r}
ggplot(NULL,aes(1:50))+geom_line(aes(y =samp1_mean), color = "black") +
     geom_line(aes(y =samp1_max), color = "red") +
    geom_line(aes(y = samp1_mid), color = "green") +
    geom_line(aes(y = samp1_min), color = "blue") + geom_line(aes(y = 0.5), color = "purple")
```



## The Normal (0, 1) distribution:
### Drawing 50 random samples:

```{r}
samp2 <- replicate(50, rnorm(25, 0, 1))
samp2
```
### Calculating mean for the above sample:

```{r}
samp2_mean <- replicate(50, mean(rnorm(25, 0, 1)))
samp2_mean
```
### Calculating minimum for each of the above samples:

```{r}
samp2_min <- replicate(50, min(rnorm(25, 0, 1)))
samp2_min
```

### Calculating maximum for each of the above samples:

```{r}
samp2_max <- replicate(50, max(rnorm(25, 0, 1)))
samp2_max
```

### Calculating median for each of the above samples:

```{r}
samp2_mid <- replicate(50, median(rnorm(25, 0, 1)))
samp2_mid
```

### Plotting these 4 statistics:


```{r}
ggplot(NULL,aes(1:50))+geom_line(aes(y =samp2_mean), color = "black") +
     geom_line(aes(y =samp2_max), color = "red") +
    geom_line(aes(y = samp2_mid), color = "green") +
    geom_line(aes(y = samp2_min), color = "blue") + geom_line(aes(y = 0), color = "purple")
```



## The Cauchy (0, 1) distribution:
### Drawing 50 random samples:

```{r}
samp3 <- replicate(50, rcauchy(25, 0, 1))
samp3
```
### Calculating mean for the above sample:

```{r}
samp3_mean <- replicate(50, mean(rcauchy(25, 0, 1)))
samp3_mean
```
### Calculating minimum for each of the above samples:

```{r}
samp3_min <- replicate(50, min(rcauchy(25, 0, 1)))
samp3_min
```

### Calculating maximum for each of the above samples:

```{r}
samp3_max <- replicate(50, max(rcauchy(25, 0, 1)))
samp3_max
```

### Calculating median for each of the above samples:

```{r}
samp3_mid <- replicate(50, median(rcauchy(25, 0, 1)))
samp3_mid
```

### Plotting these 4 statistics:

```{r}
ggplot(NULL,aes(1:50))+geom_line(aes(y =samp3_mean), color = "purple") +
     geom_line(aes(y =samp3_max), color = "red") +
    geom_line(aes(y = samp3_mid), color = "green") +
    geom_line(aes(y = samp3_min), color = "blue") 
```


### The variation of the statistics from sample to sample is called `Sample fluctuation`.

## The Normal (0, 1) distribution:
### Drawing 50 random samples:

```{r}
samp4 <- replicate(50, rnorm(100, 0, 1))
samp4
```
### Calculating mean for the above sample:

```{r}
samp4_mean <- replicate(50, mean(rnorm(100, 0, 1)))
samp4_mean
```
### Calculating minimum for each of the above samples:

```{r}
samp4_min <- replicate(50, min(rnorm(100, 0, 1)))
samp4_min
```

### Calculating maximum for each of the above samples:

```{r}
samp4_max <- replicate(50, max(rnorm(100, 0, 1)))
samp4_max
```

### Calculating median for each of the above samples:

```{r}
samp4_mid <- replicate(50, median(rnorm(100, 0, 1)))
samp4_mid
```

### Plotting these 4 statistics:


```{r}
ggplot(NULL,aes(1:50))+geom_line(aes(y =samp4_mean), color = "black") +
     geom_line(aes(y =samp4_max), color = "red") +
    geom_line(aes(y = samp4_mid), color = "green") +
    geom_line(aes(y = samp4_min), color = "blue") + geom_line(aes(y = 0), color = "purple") 
```

### Sample fluctuation decrese with increase in sample size.

```{r}
ggplot(NULL, aes(x = 1:50)) + geom_line(aes(y = samp2_mean), color = "blue") + geom_line(aes(y = samp4_mean), color = "green") + geom_line(aes(y = 0), color = "blue")
```

```{r}
ggplot(NULL, aes(x = samp2_mean)) + geom_histogram()
hist(samp2_mean)
```

```{r}
ggplot(NULL, aes(x = samp4_mean)) + geom_histogram()
hist(samp4_mean)
```


```{r}
#A = matrix(replicate(50, rnorm(25, 0, 1)))
#A1 = apply(A, 2, mean)
#A2 = apply(A, 2, median)
#A3 = apply(A, 2, min)
#A4 = apply(A, 2, max)
#matplot(1:50, cbind(A1, A2, A3, A4), type = "l", col = 1:4, x = "sample number", y = "Statistics")
#alt+ctrl+i for a R block
```


Question: Taking 50 random samples from N(0, 1) of sizes: (a) 25, (b) 200, (c) 500, (d) 1000, (e) 10000, obtain the histogram of the frequency distribution of the sample mean. Comment on your findings.

Submit to: sdg.stat@sxccal.edu

























