---
title: "Class Work"
author: "Sayan Das"
date: "2022-09-26"
output: pdf_document
---

# tibble, dplyr, tidyverse tutorial

### Calling the 'flights' dataset from the nycflights13 library
flights dataset is available in the *nycflights13* library. To use it, it should be installed into the system.
```{r}
library(nycflights13)
flights
```

### Query: Give all the flights that departed on the 1st january
Here we are going to use filter() function which Is available in the *dplyr* package. Let us first call the package. 

```{r}
library(dplyr)
```

**Syntax**  
filter(dataset name, feature where the condition is applied)  

The query can be solved In the following way.

```{r}
filter(flights, month==1, day==1)
```

### Query: Give all the flights that Departed on November or December
The query can be solved In the following way.

```{r}
filter(flights, month %in% c(11,12))

## alternative  
# filter(flights, month==11 | month==12)
```

### Find flights that were not delayed on arrival or departure by more than 2 hours
The query can be solved In the following way.

```{r}
filter(flights, arr_delay <= 120 & dep_delay <= 120)

## alternative 
# filter(flights, !(arr_delay > 120 | dep_delay > 120))
```

### Find the flights with arrival delay  of 2 or more hours
The query can be solved In the following way.

```{r}
filter(flights, arr_delay >= 120)
```

### Find the flights that flew to houston
The query can be solved In the following way.

```{r}
filter(flights, dest %in% c("IAH","HOU") )
```

### Find the flights operated by United, America or delta
The query can be solved In the following way.

```{r}
filter(flights, carrier %in% c("UA", "AA", "DL"))
```

### Find the flights that departed in Summer (July, August, September) 
The query can be solved In the following way.

```{r}
filter(flights, month %in% c(7,8,9))
```

### Find the flights that arrive more than 2 hours late but did not leave late
The query can be solved In the following way.

```{r}
filter(flights, arr_delay > 120 & dep_delay <= 0)
```

### Find that were delay by atleast an hour but made up over 30 minutes in flights
The query can be solved In the following way.

```{r}
filter(flights, arr_delay >= 60 & dep_delay - arr_delay > 30)
```

### flight that departed between midnight and 6am both inclusive
The query can be solved In the following way.

```{r}
filter(flights, dep_time >= 0 & dep_time <= 600)
## alternative
# filter(flights, between(dep_time, 0, 600)) 
```

### Find how many flights are missing departure time
The query can be solved In the following way.

```{r}
filter(flights, is.na(dep_time))
```
### From the flight dataset consider arrival delay departure delay distance and air time

Here we can use the select() function which is available inside the *dplyr* package.  

**Syntax**  
select(dataset name, feature name)  

The query can be solved In the following way.

```{r}
flight1 = select(flights, arr_delay, dep_delay, distance, air_time); flight1
```

using mutate() function we can add a column to a dataset which is a transformation of the existing columns of the dataset.  

**Syntax**  
mutate(dataset name, variable name = variable Definition)

```{r}
mutate(flight1, gain=arr_delay-dep_delay, speed=distance*60/air_time)
```

transmute() function do exactly as mutate() function but it shows the computed columns seperately  

**Syntax**
transmute(datset, variable name = variable definition)

```{r}
transmute(flights, gain=arr_delay-dep_delay, speed=distance*60/air_time)
```

### How can you compute hour and minute from departure time using transmute

```{r}
transmute(flights, hour=dep_time%/%100, minute=dep_time %% 100)
```
### note: Tibble functions
filter() (in *dplyr* library) : filter a data according to some condition  
names(): find the names of the variable in the dataset  
between() (in *dplyr* library) : condition on variable having values between two other values  
select(): used to select particular columns from a dataset  
mutate(): used to append a column in the dataset  
transmute(): used to show a tranformation on column in the dataset
