---
title: "Class Work"
author: "Sayan Das"
date: "2022-10-31"
output: pdf_document
---

# tibble, dplyr, tidyverse tutorial (continued...)

### Calling the 'flights' dataset from the nycflights13 library
flights dataset is available in the *nycflights13* library. To use it, it should be installed into the system.
```{r}
library(nycflights13)
library(dplyr)
flights
```

```{r}
small_flight = select(flights, arr_delay, dep_delay, distance, air_time)
small_flight = mutate(small_flight, gain = arr_delay-dep_delay, speed = distance/air_time*60)
```

### Query: On an average what is The departure delay? And also report the average speed
Using summarize() function we can do operation on the rows. Like we can apply average on a particular columns. 

**syntax**  
summaraise(dataset name, summarization factor name = definition )
```{r}
summarise(small_flight, avg_delay = mean(dep_delay, na.rm=TRUE), avg_speed = mean(speed, na.rm=TRUE))
```

**Similarity between mutate() and summarize()**  
Both of them  returns a dataframe in a tibble format  
Both of are doing some arithmatic operation

**Dis-similarirty between mutate() and summarize()**  
mutate() is taking vectorize function only...That is it takes a vector input and it also returns a vector output.

But in summarize() we are condensing the data, here the result need not to be vectorize.

### Query: Report the average departure delay and total departure delay for eachday
group_by() function is going to help us in this case. It helps to apply aggregate funtion for each of the values available in some column

**syntax**  
group_by(dataset name, column1, column2, column3,...) column1, column2, column3 are those column according to whose values the data should be grouped.

```{r}
day_wise = group_by(flights, year, month, day)
summarise(day_wise, avg_dep_delay = mean(dep_delay, na.rm=TRUE), tot_dep_delay = sum(dep_delay, na.rm=TRUE))
```

### Query: Compute the average departure delay grouped by day , then over month  and then by year

```{r}
(per_day = summarise(day_wise, avg_delay = mean(dep_delay, na.rm=TRUE)))
(per_month = summarise(per_day, avg_delay = mean(avg_delay, na.rm=TRUE)))
(per_year = summarise(per_month, avg_delay = mean(avg_delay, na.rm=TRUE)))
```

### Query: 
**Suppose I want to  study the relationship between the distance and average arrival delay for each destination. For this I have to  do the following steps 
1. Group all flights by destinations
2. Summarise the data to compute the average distance, average delay and no. of flights arriving in each destination
3. Filter to remove noisy points and Honolulu air which is twice as far away as the next closest airport
4. Prepare a scatter plot of average distance and average arrival delay **

Here we are going to need n() function that will be helping us to count the number of flights. 

**syntax**  
n(): (no argument needed) see example

Here noisy point means those destinations that has less or equal to 20 flights arrived.  
```{r}
dest_wise = group_by(flights, dest)
destwise_summary = summarise(dest_wise, avg_dist = mean(distance, na.rm=TRUE), avg_arr_delay = mean(arr_delay, na.rm=TRUE), flight_count=n())
filtered = filter(destwise_summary, dest != 'HNL', flight_count > 20)

library(ggplot2)

ggplot(filtered, aes(x = avg_dist, y = avg_arr_delay))+
  geom_point(colour='Red', size =1.02)+
  geom_smooth(se=FALSE)+
  labs(x = 'Average Distance', y = 'Average Arrival Delay',
       title = 'Scatterplot: Average Distance Vs Average Arrival Time',
       subtitle = 'For Several airports')
```

As the distance increases the arrival delay decreases, that means it is easier for the flights to  make up the delay when it is getting a long airtime. 

### Pipe operator %>%
pipe operator (%>%) is used when a number of functions are applied sequentially. It helps us to avoid renaming for multiple time. The result of the previous query using pipe operator is given below. 

```{r}
### previous query using pipe operator
new_data = flights %>% 
      group_by(dest) %>%
      summarise(avg_dist = mean(distance, na.rm=TRUE), 
                avg_arr_delay = mean(arr_delay, na.rm=TRUE), 
                flight_count=n()) %>%
      filter(dest != 'HNL', flight_count > 20)

library(ggplot2)
ggplot(new_data, aes(x = avg_dist, y = avg_arr_delay))+
  geom_point(colour='Red', size =1.02)+
  geom_smooth(se=FALSE)+
  labs(x = 'Average Distance', y = 'Average Arrival Delay',
       title = 'Scatterplot: Average Distance Vs Average Arrival Time',
       subtitle = 'For Several airports')
  
```
### note: Tibble functions used so far
filter(): filter a data according to some condition  
names(): find the names of the variable in the dataset  
between(): condition on variable having values between two other values  
select(): used to select particular columns from a dataset  
mutate(): used to append a column in the dataset  
transmute(): used to show a tranformation on column in the dataset  
summarise(): used to get a aggregate measure on any column  
group_by(): used to group the dataset accorning to the values of some column.
n(): used to count the number of observations 