---
title: "Class Work"
author: "Sayan Das"
date: "2022-09-27"
output: 
    pdf_document:
    includes:
        in_header: "preamble.tex"
---

### Problem 1:
\textcolor{red}{1) Draw a random sample of size n (chosen by you) from a N2(0, 0 ,1, 1, 0) distribution}  
\textcolor{red}{2) compute r (sample correlation coefficient)}  
\textcolor{red}{3) define t = $\cfrac{r\sqrt{n-2}}{\sqrt{1-r^2}}$ repeat 1 to 3 for m chosen by you}   
\textcolor{red}{plot Histogram of the frequency distribution of t}

```{r}
rm(list=ls())
library(MASS)
library(ggplot2)

n = 1000
m = 1000

Mu = c(0,0); Mu
Sigma = diag(2); Sigma 

t = 0

for(i in 1:m){
  samp = mvrnorm(n, Mu, Sigma)
  r = cor(samp[,1], samp[,2])
  t[i] = r*sqrt(n-2)/sqrt(1-r^2) 
}

ggplot(NULL, aes(x=t, y=..density..))+
    geom_histogram(binwidth=0.4, fill="#256D85", color="#256D85")+
    geom_line(aes(x=t, y=dt(t,n-2)), size=1.05, col="#06283D")+
    labs(title="Distribution of the statistic t",
         x="t", y="Frequency Density")

```

### Comments:
As the sample size(n) and no. of repeatitions increases the distribution of t which is originally a $t_{n-2}$ distribution is tending towards a standard normal.

### Problem 2:
\textcolor{red}{1) Draw a random sample of size n (chosen by you) from a N2(0, 0 ,1, 1, 0.5) distribution}  
\textcolor{red}{2) compute r (sample correlation coefficient)}  
\textcolor{red}{3) define t = $\cfrac{r\sqrt{n-2}}{\sqrt{1-r^2}}$ repeat 1 to 3 for m chosen by you}  
\textcolor{red}{plot Histogram of the frequency distribution of t}

```{r}
rm(list=ls())
library(MASS)

n = 100
m = 1000

Mu = c(0,0); Mu
Sigma = matrix(c(1,0.5,0.5,1), nrow=2); Sigma 

t = 0

for(i in 1:m){
  samp = mvrnorm(n, Mu, Sigma)
  r = cor(samp[,1], samp[,2])
  t[i] = r*sqrt(n-2)/sqrt(1-r^2) 
}

ggplot(NULL, aes(x=t, y=..density..))+
    geom_histogram(binwidth=0.4, fill="#256D85", color="#256D85")+xlim(-3,10)+
    geom_line(aes(x=seq(-3,5,0.01), y=dt(seq(-3,5,0.01),n-2)), size=1.05, col="#06283D")+xlim(-3,10)
    
```

### Comments:
As the sample size(n) and no. of repeatitions increases the distribution of t is more deviating from a standard normal.

### Problem 3: 
\textcolor{red}{1) Draw a random sample of size n (chosen by you) from a N2(0, 0 ,1, 1, 0.5) distribution}  
\textcolor{red}{2) compute r (sample correlation coefficient)}  
\textcolor{red}{3) repeat 1 -> 3  for m chosen By you}  
\textcolor{red}{plot Histogram of the frequency distribution of t}

```{r}
rm(list=ls())
library(MASS)

n = 100
m = 1000
Mu = c(0,0); Mu
Sigma = matrix(c(1,0.5,0.5,1), nrow=2); Sigma 
rho = 0.5

r = 0

for(i in 1:m){
  samp = mvrnorm(n, Mu, Sigma)
  r[i] = cor(samp[,1], samp[,2])
}

ggplot(NULL, aes(x=r, y=..density..))+
    geom_histogram(binwidth=0.04, fill="#256D85", color="#256D85")+
    geom_line(aes(x=r, y=dnorm(r, rho, sqrt(((1-rho^2)^2)/n))), size=1.05, col="#06283D")+
    labs(title="Histogram for r in large sample",
         x="r", y="Frequency Density")
```

### Comments:
As the sample size(n) and no. of repeatitions increases the distribution of r is tending towards a $N(\rho,\frac{(1-\rho^2)^2}{n})$.