---
title: "SD_Sept-20_1"
author: "Srijan Kundu"
date: "2022-09-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading library}
library(ggplot2)
theme_set(
  theme_light() + theme(legend.position = "top")
  )
library(ggpubr)
library(shiny)
```




### Generate a single observation from a $\chi^2_{(1)}$ distribution.
<ol>
  <li> Draw a single observation from $N(0,1)$
  <li> Square it to get a single observation.
</ol>

```{r}

```

### Generate 5 independent observations from a $\chi^2_{(1)}$ distribution.
<ol>
  <li> Generate $5$ observations from $N(0,1)$
  <li> Square them
</ol>

```{r}

```
### Generate a single observation from a $\chi^2_{(5)}$ distribution.
<ol>
  <li> Generate $5$ observations from $N(0,1)$
  <li> Square them, then add them
</ol>
```{r}

```
### Generate 5 observations from a $\chi^2_{(5)}$ distribution.
<ol>
  <li> Generate $25$ observations from $N(0,1)$
  <li> Square them, group them in 5 element sets, then add them.
</ol>
```{r}

```
### Draw 100 random samples each of size 10 from a $\chi^2_{(5)}$ distribution.
```{r}

```



### Shape of $\chi^2_{(5)}$ distribution.
```{r}
pl1 = ggplot(data.frame(x = c(0, 100)), aes(x = x)) +
     stat_function(fun = dchisq, args = list(df = 5)) + xlab("df = 5") + ylab("density") 
pl2 = ggplot(data.frame(x = c(0, 100)), aes(x = x)) +
     stat_function(fun = dchisq, args = list(df = 10)) + xlab("df = 10") + ylab("density")
pl3 = ggplot(data.frame(x = c(0, 100)), aes(x = x)) +
     stat_function(fun = dchisq, args = list(df = 15)) + xlab("df = 15") + ylab("density")
pl4 = ggplot(data.frame(x = c(0, 100)), aes(x = x)) +
     stat_function(fun = dchisq, args = list(df = 25)) + xlab("df = 25") + ylab("density")
pl5 = ggplot(data.frame(x = c(0, 100)), aes(x = x)) +
     stat_function(fun = dchisq, args = list(df = 50)) + xlab("df = 50") + ylab("density")
```

```{r}
ggarrange(pl1, pl2, pl3, pl4, pl5)
```

### Comment on the nature of the limiting distribution of $\frac{Y-n}{\sqrt{2n}}$ where $Y \sim \chi^2_{(n)}$.
```{r}
samp1 = as.data.frame(rchisq(50, 5))
samp11 = (samp1 - 5)/sqrt(2*5)

typeof(samp11)
sample = samp11 - 5
sample = sample / 5
typeof(sample)
as.data.frame(sample)
typeof(sample)
names(sample) <- "samples"
sample
```





































