---
title: "SC_MD_Nov-07_1"
author: "Srijan Kundu"
date: "2022-11-07"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(matlib)
library(pracma)
```

## Question 1: Suppose we want to generate $20$ random observations from a $N(2, 1)$ distribution, and compute the mean of those observations.

```{r}
samp1 = rnorm(20, 2, 1)
samp1
mean(samp1)
```

## Question 2: Suppose we want to repeat this procedure $R = 10$ times.

> **Steps:**
>
> 1\. Draw a random sample of size $n = 20$ from $N(2, 1)$ distribution.
>
> 2\. Compute mean of the observations from *step 1*.
>
> 3\. Repeat *Step 1 and 2* $R$ times.

To perform such repetitive tasks, we can make use of the function `replicate`.

The syntax is: `replicate(n, expr)`; where `n` stands for the number of replications, and `expr` stands for the expression that we have to evaluate multiple times.

```{r}
R1 = 10
samp2 = replicate(R1, mean(rnorm(20, 2, 1)))
samp2
```

## Question 3: Suppose we want to compute the mean of these $R$ sample means, and the variance.

```{r}
mean(samp2)
var(samp2)
(R1-1)*var(samp2)/R1
```

## Question 4: Make $R = 100$, similarly as above, find the mean, var and draw the histogram.

```{r}
R2 = 100000
samp3 = replicate(R2, mean(rnorm(20, 2, 1)))
#hist(samp3, freq = FALSE)
ggplot(data = NULL, aes(x = samp3)) + geom_histogram(aes(y=..density..)) +geom_density(colour = "cyan")
```

### *Suppose we want to write a program for the same problem using a user defined function.*

-   The syntax for an user defined function is as below:

    f = function(x){

    x\*x\*x

    }

-   Here, f(x) returns $x^3$.

```{r demo}
f1 = function(x){
  x^3
}
u = 1:4
f1(u)
```

> Note that here `f` is the name of the function given by the user and `x` is the argument, which can be a scalar or a vector. The function must be enclosed within {}. The argument inside the function and outside the function need not be given the same name, but they must be of the same type.

```{r demo function}
f2 = function(x){
  n = 5
  x^3+n
}
u = 1:4
f2(u)
#n
```
Remember that all the constants must be defined globally (outisde the function) so that they can be used for other purposes outside the function.
```{r}
n = 5
f3 = function(x){
  x^3+n
}
u = 1:4
f3(u)
n
```
## Question 5: Generate a random sample of size $n= 10, 50, 100, 200, 500$ from a $N(2, 1)$ dist. and compute its mean. Repeat this procedure $1000$ times, compute the mean and the variance of the $1000$ samples means.
```{r}
R3 = 1000
f4 = function(n){
  mean(rnorm(n, 2, 1))
}
n = c(10, 50, 100, 500)
v1 = c(mean(replicate(R3, f4(10))), mean(replicate(R3, f4(50))), mean(replicate(R3, f4(100))), mean(replicate(R3, f4(500))))
v2 = c(var(replicate(R3, f4(10))), var(replicate(R3, f4(50))), var(replicate(R3, f4(100))), var(replicate(R3, f4(500))))
data.frame(Sample_Size = n, Means = v1, Variances = v2)
```
_or,_
```{r}
f5 = function(n, R, mu, sigma){
  g_m = g_v = array(0)
  for(i in seq_along(n))
  {
    x = replicate(R, mean(rnorm(n[i], mu, sigma)))
    g_m[i] = mean(x)
    g_v[i] = var(x)*(R-1)/R
  }
  return(data.frame(sample_size = n, Grand_means = g_m, Grand_variances = g_v))
}
f5(c(10, 50, 100, 500), 1000, 2, 1)
```
_or,_
```{r}
k = 4
R = 1000
L = function(n){
  u = replicate(R, mean(rnorm(n, 2, 1)))
  m = mean(u)
  v = var(u)*(R-1)/R
  answer = c(n, m, v)
  answer
}
M = matrix(0, k, 3)
n = c(10, 50, 100, 200)
for(i in 1:k)
{
  M[i,] = L(n[i])
}
colnames(M) = c("Sample Size", "Mean", "Variance")
M
```
```{r}
x = rnorm(100)
y = ifelse(x>0, 1, 0)
y
```

```{r}
x = rnorm(100)
y = ifelse(x<0, 1, ifelse(x>1 & x < 1.5, 2, ifelse(x > 1.5, 3, 4)))
data.frame(x, y)
```



