---
title: "DS_Nov_10-Graphics_Using_ggplot-2"
author: "Srijan Kundu"
date: "2022-11-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
set.seed(1)
library(dplyr)
library(ggplot2)
```

The dataset which will be used here is the `economics` dataset.
```{r}
economics
```
### Scatterplot number of unemployed against time.
```{r}
qplot(date, unemploy, data = economics)
```
> But, for time-series data, a line plot should be used.

```{r}
qplot(date, unemploy, data = economics, geom = c("line"))
#ggplot(data = economics, aes(x = date, y = unemploy)) + geom_line()
```
### Display both the points and the lines
```{r}
qplot(date, unemploy, data = economics, geom = c("point", "line"))
#ggplot(data = economics, aes(x = date, y = unemploy)) + geom_line() + geom_point()
```

### Change the x-axis label to "DATE", give a proper y-axis title and a proper plot-title.
```{r}
qplot(date, unemploy, data = economics, geom = c("line"), xlab = "Date", ylab = "Unemployemnt", main = "Date ~ Unemployment time-series plot")
```
### Change the x axis intervals to 5 years.
```{r}
qplot(date, unemploy, data = economics, geom = c("line"), xlab = "Date", ylab = "Unemployemnt", main = "Date ~ Unemployment time-series plot")
```

### Obtain a line diagram showing number of unemployed as well 

