---
title: "DS_Nov_10-Graphics_Using_ggplot-1"
author: "Srijan Kundu"
date: "2022-11-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
set.seed(1)
library(dplyr)
library(ggplot2)
```

### The dataset that will be used to demonstrate are `diamonds` dataset.

```{r}
diamonds
```
### The scales of measurements are given as `dbl` or `ord` as ordinal etc.

```{r}
head(diamonds)
glimpse(diamonds)
```
### Obtain a random sample of 1000 rows from the `diamond` dateset.
```{r}
sample = slice_sample(diamonds,  n = 1000)
sample
```
### Obtain a scatterplot of price against carat from this sample. Use the `qplot` function.
```{r}
qplot(carat, price, data = sample)
#ggplot(sample, aes(x = carat, y = price)) + geom_point()
```
### Faceting is subseting the data and using different plots for each characteistic. But, here we want to see which point corresponds to which color in the same scatterplot demonstrated above.
```{r}
qplot(carat, price, data = sample, color = color)
```
#### Same thing as above using `clarity`:
```{r}
qplot(carat, price, data = sample, color = clarity)
```
### Show different "cuts" is different shapes
```{r}
qplot(carat, price, data = sample, color = color, shape = cut)
```
### Make points in the bottom left corner brighter than those in the top right corner, or control the transperancy.
```{r}
qplot(carat, price, data = sample, color = color, alpha = I(0))
qplot(carat, price, data = sample, color = color, alpha = I(0.25))
qplot(carat, price, data = sample, color = color, alpha = I(0.5))
qplot(carat, price, data = sample, color = color, alpha = I(0.75))
qplot(carat, price, data = sample, color = color, alpha = I(1))
```

### Try using bar diagram for frequency distribution for different colors.
```{r}
qplot(color, data = diamonds, fill = color)
#ggplot(diamonds, aes(x = color, fill = color)) + geom_bar()
```
### Change the vertical bars to horizontal bars.
```{r}
plot = qplot(color, data = diamonds, fill = color)
plot + coord_flip()     #this is called layering
```
### For each type of cut, obtain freq dist of number of different colors.
```{r}
qplot(color, data = sample, fill = color, geom = "bar") + facet_grid(~cut)
```
### Use subdevided bars
```{r}
#qplot(color, data = diamonds, fill = color, geom = "bar", )
ggplot(diamonds, aes(fill = color, x = cut)) + geom_bar(position="fill")
```

### Obtain a boxplot of the price of diamonds for each cut of diamonds
```{r}
#for the entire dataset
qplot(price, data = diamonds, fill = color, geom = "boxplot") + facet_grid(~cut)
qplot(price, data = sample, color = cut, geom = "boxplot") + facet_grid(~cut)
```

