---
title: "Poisson Fitting AC Nov 15-16-18-22"
author: "Soumyadeep Poddar"
date: "2022-11-15"
output: html_document
---

### Fitting a poisson distribution and commenting on nature of fit.

Question:

```{r}
social_class <- c("LP","Working class","Artisans","Shopkeeper","White collar","Ideological Professions")
age_0=c(13,98,33,25,87,42)
age_1=c(31,217,69,50,184,90)
age_2=c(40,179,68,43,106,30)
age_3=c(31,124,36,25,38,12)
age_4=c(18,61,24,7,22,4)
age_5=c(22,54,14,9,21,4)
data=data.frame(social_class,age_0,age_1,age_2,age_3,age_4,age_5)
data
```

Solution:

Entering ages as $x$ variable.

```{r}
x <- c(0,1,2,3,4,5)
```

For Lumpen-proletariat.

```{r}
obs_freq <- c(13,31,40,31,18,22)
N=sum(obs_freq)
mean <-  sum(x * obs_freq)/sum(obs_freq)
prob=c()
exp_freq=c()
prob=dpois(x,mean)
exp_freq=prob * sum(obs_freq)
gfit=((obs_freq-exp_freq)^2)/exp_freq
table1=data.frame(x,prob,obs_freq,exp_freq,gfit)
table1
obs_chi_1=sum(gfit)
s_2=sum((((x-mean)^2)*obs_freq))/(N-1)
x_by_s2=mean/s_2
x_by_s2
```

For Working class:

```{r}
obs_freq <- c(98,217,179,124,61,54)
mean <-  sum(x * obs_freq)/sum(obs_freq)
prob=c()
exp_freq=c()
prob=dpois(x,mean)
exp_freq=prob * sum(obs_freq)
gfit=((obs_freq-exp_freq)^2)/exp_freq
sum(gfit)
table2=data.frame(x,prob,obs_freq,exp_freq,gfit)
table2
s_2=sum((((x-mean)^2)*obs_freq))/(N-1)
x_by_s2=mean/s_2
x_by_s2
```

For Artisans

```{r}
obs_freq <- c(33,69,68,36,24,14)
mean <-  sum(x * obs_freq)/sum(obs_freq)
prob=c()
exp_freq=c()
prob=dpois(x,mean)
exp_freq=prob * sum(obs_freq)
gfit=((obs_freq-exp_freq)^2)/exp_freq
sum(gfit)
table3=data.frame(x,prob,obs_freq,exp_freq,gfit)
table3
s_2=sum((((x-mean)^2)*obs_freq))/(N-1)
x_by_s2=mean/s_2
x_by_s2
```

For Shopkeeper

```{r}
obs_freq <- c(25,50,43,25,7,9)
mean <-  sum(x * obs_freq)/sum(obs_freq)
prob=c()
exp_freq=c()
prob=dpois(x,mean)
exp_freq=prob * sum(obs_freq)
gfit=((obs_freq-exp_freq)^2)/exp_freq
table3=data.frame(x,prob,obs_freq,exp_freq,gfit)
table3
s_2=sum((((x-mean)^2)*obs_freq))/(N-1)
x_by_s2=mean/s_2
x_by_s2
```

For White collar

```{r}
obs_freq <- c(87,184,106,38,22,21)
mean <-  sum(x * obs_freq)/sum(obs_freq)
prob=c()
exp_freq=c()
prob=dpois(x,mean)
exp_freq=prob * sum(obs_freq)
gfit=((obs_freq-exp_freq)^2)/exp_freq
obs_chi_5=sum(gfit)
table4=data.frame(x,prob,obs_freq,exp_freq,gfit)
table4
s_2=sum((((x-mean)^2)*obs_freq))/(N-1)
x_by_s2=mean/s_2
x_by_s2
```

For ideological professions:

```{r}
obs_freq <- c(42,90,30,12,4,4)
mean <-  sum(x * obs_freq)/sum(obs_freq)
prob=c()
exp_freq=c()
prob=dpois(x,mean)
exp_freq=prob * sum(obs_freq)
gfit=((obs_freq-exp_freq)^2)/exp_freq
table4=data.frame(x,prob,obs_freq,exp_freq,gfit)
table4
s_2=sum((((x-mean)^2)*obs_freq))/(N-1)
x_by_s2=mean/s_2
x_by_s2
```

## NOV 18

#### Fit a geometric distribution to the given data

```{r}
#Question: 
months <- c(1:24)
data <- c(52,46,50,27,15,12,8,4,5,1,0,2,1,0,0,2,2,1,5,1,4,1,1,0)
data.frame(months,data)
```

```{r}
N=sum(data)
N
mean_x <- (sum(months * data))/N 
mean_x
s_sq <- (sum(months * months * data) - (N * (mean_x) ^ 2))/(N-1)

p_hat <- mean_x/s_sq
p_hat
q_hat <- 1 - p_hat

prob <- c()
prob <- dgeom(months-1,p_hat)
prob

exp_freq <- c()
exp_freq <- N * prob

exp_freq

data.frame(months,data,prob,exp_freq)

#chi square test
t <- sum(((data - N * prob) ^ 2)/(N * prob))
t
```

Nov 22

Plot the following Binomial distributions and comment on their skewness.

```{r}
library(ggplot2)
```

i) Bin(20,1/6)

```{r}

x <- 0:20
prob <- dbinom(x,20,(1/6))
df <- data.frame(x,prob)
p1 <- ggplot(df,mapping=aes(x=x,y=prob))+ geom_col(colour="blue")+ labs(title = "Binomial(20,1/6)",x="x",y="P(X=x)")

p1
```

ii) Bin(20,1/2)

```{r}
x <- 0:20
prob <- dbinom(x,20,0.5)
df <- data.frame(x,prob)
p2 <- ggplot(df,mapping=aes(x=x,y=prob))+ geom_col(colour="purple")+ labs(title = "Binomial(20,1/2)",x="x",y="P(X=x)" )
p2
```


iii) Bin(20,5/6)

```{r}
x <- 0:20
prob <- dbinom(x,20,(5/6))
df <- data.frame(x,prob)
p3 <- ggplot(df,mapping=aes(x=x,y=prob))+ geom_line(colour="blue")+ labs(title = "Binomial(20,5/6)",x="x",y="P(X=x)")
p3
```

```{r}

```

