---
title: "DS_Nov_22_1"
author: "Srijan Kundu"
date: "2022-11-22"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Loading `diamonds` dataset:

```{r}
diamonds
glimpse(diamonds)
```

## Random sampling $2000$ rows from `diamonds`:

```{r}
data_dia = slice_sample(diamonds, n = 2000)
```

### Obtain a scatterplot of the carat and the price:

```{r}
p1 = ggplot(data_dia, aes(x = carat, y = price))
p1 + geom_point()
```

### Represent the points in the scatterplot by the specific colors of the specific diamonds:

```{r}
p1 + geom_point(aes(color = color))
```

### Indicate different colors of different diamonds by different shapes:

```{r}
p1 + geom_point(aes(shape = color))
```

### Try size to distinguish as well:

```{r}
p1 + geom_point(aes(size = color))
```

### Use both color and shape to distinguish:

```{r}
p1 + geom_point(aes(shape = color, color = color))
```

### Different scatterplots on the basis of different colors of diamonds:

```{r}
p1 + geom_point(aes(color = color)) + facet_grid(~color)
p1 + geom_point(aes(color = color)) + facet_wrap(~color)
p1 + geom_point(aes(color = color)) + facet_wrap(vars(color))
```

### Obtain barplot of the frequency distribution of the colors:

```{r}
p2 = ggplot(diamonds, aes(x = color, fill = color)) 
p2 + geom_bar()
```

### Modify the bar width:

```{r}
p2 + geom_bar(width = 0.5)
p2 + geom_bar(width = 1)
p2 + geom_bar(width = 10)
p2 + geom_bar(color = "black")
```

### Make the bar diagram horizontal:

```{r}
p2 + geom_bar() + coord_flip()
```

### Within each color, consider the frequency distribution of different clarity (do in same graph, first in horizontally placed bars and then for stacked for each color):

```{r}

```

###  
