---
title: "DB_Nov02_01"
author: "Srijan Kundu"
date: "2022-11-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(matlib)
library(pracma)
```

## Question 1:
```{r}
M = matrix(c(1,1,1,1,1,2,3,4,1,3,6,10,1,4,10,20),nrow = 4 ,byrow = T)
M
```
### Question 1a: Trace of M.
```{r}
tr(M)
```
### Quetion 1b: Rank of M
```{r}
R(M)
```
### Question 1c: Inverse of M
```{r}
inv(M)
```
### Question 1d: Det of M using the functions `Det(A)` and `cofactor(A, i, j)`.
```{r}
Det(M)
```
```{r}
d = 0
for (i in 1:4){
  d = d + M[1,i]*cofactor(M, 1, i)
}
d
```
## Question 2: Apply Gram-Schmidt orthogonalization to the following sequene of vectors:
```{r}
V = matrix(c(1,2,0,8,1,6,0,0,1), nrow = 3, byrow = F)
GM = GramSchmidt(V, normalize = F, verbose = F, tol = sqrt(.Machine$double.eps))
GM
```
## Question 3: Check whether the following vectors are independent:
### 3.(i) (2,3,1), (1,0,4), (2,4,1), (0, 3, 2).
```{r}
M1 = matrix(c(2,3,1,1,0,4,2,4,1,0,3,2), nrow = 3, byrow = F)
R(M1)
```
Rank of the matrix formed by the given vectors(3) are less than number of vectors(4); hence the given vectors are not independent.

### 3.(ii)	(1, 3, −1, 0), (2, 9, −1, 3), (4, 5, 6, 11), (1, −1, 2, 5), (3, −2, 6, 7).
```{r}
M2 = matrix(c(1,3,-1,0,2,9,-1,3,4,5,6,11,1,-1,2,5,3,-2,6,7), nrow = 4, byrow = F)
R(M2)
```
The given vectors are independent.

### 3. (iii) (1,1,0), (3,0,1), (5,2,1)
```{r}
M3 = matrix(c(1,1,0,3,0,1,5,2,1), nrow = 3, byrow = F)
R(M3)
```
The given vectors are not independent.

### 3.(iv) (1,4,1,7), (3,-5,2,3), (2,-1,6,9), (-2,3,1,6)
```{r}
M4 = matrix(c(1,4,1,7,3,-5,2,3,2,-1,6,9,-2,3,1,6), nrow = 4, byrow = F)
R(M4)
```
The given vectors are independent.

## Question 4:
### 4.(i)
```{r}
A1 = matrix(c(1,-1,13,2,2,-1,15,1,3,-1,17,0,1,-1,-1,-3), nrow = 4, byrow = T)
R(A1)
rref(A1)
t(A1)
rref(t(A1))
```
Rank of A is 3.

Column 4 of `rref(A1)` is linear combination of the other 3 columns.
Hence, the column space of A is spanned by (1, 2, 3, 1), (-1, -1, -1, -1), (13, 15, 17, -1).

Column 3 of `rref(t(A1))` is linear combination of the other 3 columns. Hence, the row space of A is spanned by (1, -1, 13, 2), (2, -1, 15, 1), (1, -1, -1, -3).

The basis of null space of A is the column 4 of `rref(A1)`.

The basis of the left null space of A is 

### 4.(ii)
```{r}
B1 = matrix(c(5,10,15,20,25,30,1,2,3,4,5,6,7,9,11,13,15,17,50,49,48,47,46,45,-5,-6,-7,-8,-9,-10), nrow = 5, byrow = T)
R(B1)
rref(B1)
t(B1)
rref(t(B1))
```
The rank of B is 2.

Columns 3, 4, 5, 6 of `rref(B1)` are some linear combinations of columns 1 and 2; hence a basis of the column space of B would be: (5, 1, 7, 50, -5), (10, 2, 9, 49, -6).

Columns 2, 4, 5 of `rref(t(B1))` are some linear combinations of columns 1 and 3; hence a basis of the row space of B would be: (5, 10, 15, 20, 25, 30), (7, 9, 11, 13, 15, 17).

The basis of the null space of B is the 

### Find the orthogonal basis for the row space of the matrix A in 4(i).
```{r}
#Gram-Schmidt orthogonalization on basis vectors of row space of A
C = matrix(c(1,-1,13,2,2,-1,15,1,1,-1,-1,-3), nrow = 4, byrow = F)
GramSchmidt(C, normalize = F, verbose = F, tol = sqrt(.Machine$double.eps))
```
The columns of the matrix above form an orthogonal basis of row space of A.