---
title: "DS_Assignment_1"
author: "Srijan Kundu"
date: "Nov 13, 2022"
output: pdf_document
---

```{r}
library("ie2misc")
library("stats")
```

## Question:

Carry out $steps\;1 - 5$ for the following distributions:

1.  $N(0, 1)$,
2.  $Cauchy(0, 1)$,
3.  $LogNormal(0, 1)$,
4.  $Gamma(1, \frac1 2)$,
5.  $Beta(3, 3)$,
6.  $Beta(3, 1)$,
7.  $Beta(\frac 1 2, 3)$,
8.  $t_5$,
9.  $t_{20}$.

### Steps:

1.  Draw a random sample of size $n$ from $\displaystyle f_{\theta}(x)$.
2.  Compute the following quantities:
    i)  the ratio $\displaystyle \frac{\bar{x}-mode(x)}{\bar{x} - median(x)}$,
    ii) the ratio $\displaystyle \frac{MD_{\bar{x}}}{sd(x)}$,
    iii) the ratio $\displaystyle \frac{SIQR(x)}{SD(x)}$,
    iv) $\%$ of observations in the interval $\displaystyle \bar{x} \pm 6\times SD$,
    v)  $\%$ of observations in the interval $\displaystyle \bar{x} \pm 7.5\times MD_{\bar{x}}$,
    vi) $\%$ of observations in the interval $\displaystyle \bar{x} \pm 9\times QD$.
3.  Repeat $steps\;1-2$ for $R = 1000$ times. This will generate $R$ values for each sets of quantities computed in $step\;2$.
4.  For each of the quantities obtained in $step\;2$, repeat the minimum and maximum value in the form of an interval.
5.  Carry out $steps\;1-4$ for $n = 10, 100, 1000, 5000$.

------------------------------------------------------------------------

## Answer:

```{r}
n = c(10, 100, 1000, 5000)
R = 1000
```

### Data collection and preparation for manipulation:

```{r data_preparation]]}
data1 = array(NA, c(9, 10, 1000))
data2 = array(NA, c(9, 100, 1000))
data3 = array(NA, c(9, 1000, 1000))
data4 = array(NA, c(9, 5000, 1000))

data1[1, , ] = replicate(R, rnorm(n[1], 0, 1))
data1[2, , ] = replicate(R, rcauchy(n[1], 0, 1))
data1[3, , ] = replicate(R, rlnorm(n[1], 0, 1))
data1[4, , ] = replicate(R, rgamma(n[1], shape = 1, scale = 0.5))
data1[5, , ] = replicate(R, rbeta(n[1], 3, 3))
data1[6, , ] = replicate(R, rbeta(n[1], 3, 1))
data1[7, , ] = replicate(R, rbeta(n[1], 0.5, 3))
data1[8, , ] = replicate(R, rt(n[1], 5))
data1[9, , ] = replicate(R, rt(n[1], 20))

data2[1, , ] = replicate(R, rnorm(n[2], 0, 1))
data2[2, , ] = replicate(R, rcauchy(n[2], 0, 1))
data2[3, , ] = replicate(R, rlnorm(n[2], 0, 1))
data2[4, , ] = replicate(R, rgamma(n[2], shape = 1, scale = 0.5))
data2[5, , ] = replicate(R, rbeta(n[2], 3, 3))
data2[6, , ] = replicate(R, rbeta(n[2], 3, 1))
data2[7, , ] = replicate(R, rbeta(n[2], 0.5, 3))
data2[8, , ] = replicate(R, rt(n[2], 5))
data2[9, , ] = replicate(R, rt(n[2], 20))

data3[1, , ] = replicate(R, rnorm(n[3], 0, 1))
data3[2, , ] = replicate(R, rcauchy(n[3], 0, 1))
data3[3, , ] = replicate(R, rlnorm(n[3], 0, 1))
data3[4, , ] = replicate(R, rgamma(n[3], shape = 1, scale = 0.5))
data3[5, , ] = replicate(R, rbeta(n[3], 3, 3))
data3[6, , ] = replicate(R, rbeta(n[3], 3, 1))
data3[7, , ] = replicate(R, rbeta(n[3], 0.5, 3))
data3[8, , ] = replicate(R, rt(n[3], 5))
data3[9, , ] = replicate(R, rt(n[3], 20))

data4[1, , ] = replicate(R, rnorm(n[4], 0, 1))
data4[2, , ] = replicate(R, rcauchy(n[4], 0, 1))
data4[3, , ] = replicate(R, rlnorm(n[4], 0, 1))
data4[4, , ] = replicate(R, rgamma(n[4], shape = 1, scale = 0.5))
data4[5, , ] = replicate(R, rbeta(n[4], 3, 3))
data4[6, , ] = replicate(R, rbeta(n[4], 3, 1))
data4[7, , ] = replicate(R, rbeta(n[4], 0.5, 3))
data4[8, , ] = replicate(R, rt(n[4], 5))
data4[9, , ] = replicate(R, rt(n[4], 20))
```

### Functions initialization:

```{r function_creation}
getmode <- function(v) #for mode calculation
{
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}

f1 = function(data)   #1_to_calculate_2(i)
{
  return(mean(data) - getmode(data)/(mean(data) - median(data)))
}
f2 = function(data)   #2_to_calculate_2(ii)
{
  return(madstat(data)/sd(data))
}
f3 = function(data)   #3_to_calculate_2(iii)
{
  return((quantile(data, 0.75)-quantile(data, 0.25))/2*sd(data))
}
f4 = function(data)   #4_to_calculate_2(iv)
{
  return(100*sum(data > (mean(data) - 6*sd(data)) & data < (mean(data) + 6*sd(data)) )/1000)
}
f5 = function(data)   #5_to_calculate_2(v)
{
   return(100*sum(data > (mean(data) - 7.5*madstat(data)) & data < (mean(data) + 7.5*madstat(data)) )/1000)
}
f6 = function(data)   #6_to_calculate_2(vi)
{
   return(100*sum(data > (mean(data) - 9*(quantile(data, 0.75)-quantile(data, 0.25))/2) & data < (mean(data) + 9*(quantile(data, 0.75)-quantile(data, 0.25))/2))/1000)
}
```

### (i) For the ratio $\displaystyle \frac{\bar{x}-mode(x)}{\bar{x} - median(x)}$:

```{r}
vect1 = array(NA, c(4, 9, 1000))
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect1[1, i, j] = f1(data1[i, , j])  #1
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect1[2, i, j] = f1(data2[i, , j])  #2
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect1[3, i, j] = f1(data3[i, , j])  #3
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect1[4, i, j] = f1(data4[i, , j])  #4
  }
}

m1 = array(NA, c(4, 9, 2))
for (i in 1:4)
{
  for (j in 1:9)
  {
    m1[i, j, ] = c(min(vect1[i, j, ]), max(vect1[i, j, ]))
  }
}

data.frame("Sample_size" = n, "dist1" = m1[, 1, ], "dist2"= m1[, 2, ], "dist3" = m1[, 3, ], "dist4" = m1[, 4, ], "dist5" = m1[, 5, ], "dist6" = m1[, 6, ], "dist7" = m1[, 7, ], "dist8" = m1[, 8, ], "dist9" = m1[, 9, ])
```

### (ii) For the ratio $\displaystyle \frac{MD_{\bar{x}}}{sd(x)}$:

```{r}
vect2 = array(NA, c(4, 9, 1000))
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect2[1, i, j] = f2(data1[i, , j])  #1
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect2[2, i, j] = f2(data2[i, , j])  #2
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect2[3, i, j] = f2(data3[i, , j])  #3
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect2[4, i, j] = f2(data4[i, , j])  #4
  }
}

m2 = array(NA, c(4, 9, 2))
for (i in 1:4)
{
  for (j in 1:9)
  {
    m2[i, j, ] = c(min(vect2[i, j, ]), max(vect2[i, j, ]))
  }
}

data.frame("Sample_size" = n, "dist1" = m2[, 1, ], "dist2"= m2[, 2, ], "dist3" = m2[, 3, ], "dist4" = m2[, 4, ], "dist5" = m2[, 5, ], "dist6" = m2[, 6, ], "dist7" = m2[, 7, ], "dist8" = m2[, 8, ], "dist9" = m2[, 9, ])
```

### (iii) For the ratio $\displaystyle \frac{SIQR(x)}{SD(x)}$:

```{r}
vect3 = array(NA, c(4, 9, 1000))
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect3[1, i, j] = f3(data1[i, , j])  #1
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect3[2, i, j] = f3(data2[i, , j])  #2
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect3[3, i, j] = f3(data3[i, , j])  #3
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect3[4, i, j] = f3(data4[i, , j])  #4
  }
}

m3 = array(NA, c(4, 9, 2))
for (i in 1:4)
{
  for (j in 1:9)
  {
    m3[i, j, ] = c(min(vect3[i, j, ]), max(vect3[i, j, ]))
  }
}

data.frame("Sample_size" = n, "dist1" = m3[, 1, ], "dist2"= m3[, 2, ], "dist3" = m3[, 3, ], "dist4" = m3[, 4, ], "dist5" = m3[, 5, ], "dist6" = m3[, 6, ], "dist7" = m3[, 7, ], "dist8" = m3[, 8, ], "dist9" = m3[, 9, ])
```

### (iv) For $\%$ of observations in the interval $\displaystyle \bar{x} \pm 6\times SD$:

```{r}
vect4 = array(NA, c(4, 9, 1000))
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect4[1, i, j] = f4(data1[i, , j])  #1
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect4[2, i, j] = f4(data2[i, , j])  #2
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect4[3, i, j] = f4(data3[i, , j])  #3
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect4[4, i, j] = f4(data4[i, , j])  #4
  }
}

m4 = array(NA, c(4, 9, 2))
for (i in 1:4)
{
  for (j in 1:9)
  {
    m4[i, j, ] = c(min(vect4[i, j, ]), max(vect4[i, j, ]))
  }
}

data.frame("Sample_size" = n, "dist1" = m4[, 1, ], "dist2"= m4[, 2, ], "dist3" = m4[, 3, ], "dist4" = m4[, 4, ], "dist5" = m4[, 5, ], "dist6" = m4[, 6, ], "dist7" = m4[, 7, ], "dist8" = m4[, 8, ], "dist9" = m4[, 9, ])
```

### (v) For $\%$ of observations in the interval $\displaystyle \bar{x} \pm 7.5\times MD_{\bar{x}}$:

```{r}
vect5 = array(NA, c(4, 9, 1000))
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect5[1, i, j] = f5(data1[i, , j])  #1
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect5[2, i, j] = f5(data2[i, , j])  #2
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect5[3, i, j] = f5(data3[i, , j])  #3
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect5[4, i, j] = f5(data4[i, , j])  #4
  }
}

m5 = array(NA, c(4, 9, 2))
for (i in 1:4)
{
  for (j in 1:9)
  {
    m5[i, j, ] = c(min(vect5[i, j, ]), max(vect5[i, j, ]))
  }
}

data.frame("Sample_size" = n, "dist1" = m5[, 1, ], "dist2"= m5[, 2, ], "dist3" = m5[, 3, ], "dist4" = m5[, 4, ], "dist5" = m5[, 5, ], "dist6" = m5[, 6, ], "dist7" = m5[, 7, ], "dist8" = m5[, 8, ], "dist9" = m5[, 9, ])
```

### (vi) For $\%$ of observations in the interval $\displaystyle \bar{x} \pm 9\times QD$:

```{r}
vect6 = array(NA, c(4, 9, 1000))
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect6[1, i, j] = f6(data1[i, , j])  #1
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect6[2, i, j] = f6(data2[i, , j])  #2
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect6[3, i, j] = f6(data3[i, , j])  #3
  }
}
for (i in 1:9)
{
  for (j in 1:1000)
  {
    vect6[4, i, j] = f6(data4[i, , j])  #4
  }
}

m6 = array(NA, c(4, 9, 2))
for (i in 1:4)
{
  for (j in 1:9)
  {
    m6[i, j, ] = c(min(vect6[i, j, ]), max(vect6[i, j, ]))
  }
}

data.frame("Sample_size" = n, "dist1" = m6[, 1, ], "dist2"= m6[, 2, ], "dist3" = m6[, 3, ], "dist4" = m6[, 4, ], "dist5" = m6[, 5, ], "dist6" = m6[, 6, ], "dist7" = m6[, 7, ], "dist8" = m6[, 8, ], "dist9" = m6[, 9, ])
```
