---
title: "Linear Algebra Problem Set 5"
author: "Soumyadeep Poddar"
date: "2022-11-09"
output: html_document
---

install.packages("matlib")
```{r}
library(matlib)
library(pracma)
```

### 1.	Plot the following system of linear equations and comment on solvability:

#### i) The equations are as follows:
```{r}
A1=matrix(c(5,-4,-1,1),2,2,byrow=T)
b1=c(-10,2)
showEqn(A1,b1)

```

After plotting:

```{r}
plotEqn(A1,b1)
```

We see that the lines intersect and the two equations are solvable.

```{r}
Solve(A1,b1,verbose=T)
```

So, the value of  $x_1$ is -2 and $x_2$ is 0. 

#### ii) The equations are as follows:

```{r}
A2=matrix(c(1,-2,3,-6),2,2,byrow=T)
b2=c(1,3)
showEqn(A2,b2)
```
After plotting:

```{r}
plotEqn(A2,b2)
```

The two lines doesn't intersect so this system is unsolvable.


#### iii) The equations are as follows:

```{r}
A3=matrix(c(1,-2,3,-6),2,2,byrow=T)
b3=c(1,11)
showEqn(A3,b3)
```
After plotting:

```{r}
plotEqn(A3,b3)
```

The lines are parallel and there is no intersection.

The system is unsolvable.


#### iv) The equations are:
 
```{r}
A4=matrix(c(1,-1,2,2,3,1),byrow=T,3,2)
b4=c(2,1,6)
showEqn(A4,b4)
```

After plotting:

```{r}
plotEqn(A4,b4)
```

The three equations do not intersect at the same point, so the system is not solvable.

```{r}
Solve(A4,b4,verbose=TRUE)
```
We see that the system is inconsistent.

#### v) The equations are:

```{r}
A5=matrix(c(13,-4,2,-4,11,-2,2,-2,8),3,3,byrow=T)
b5=c(1,2,6)
showEqn(A5,b5)
```

After plotting:
```{r}
plotEqn3d(A5,b5)
```

The three equations intersect at a common point. Hence, it is solvable.

```{r}
Solve(A5,b5,verbose=T)
```

The values are $x_1$=0.05882353 , $x_2$=0.35294118 and $x_3$=0.82352941.

#### 4.	Solve the following system of equation using Gaussian elimination, LU factorization and QR factorization:

QR factorization.

```{r}
A=matrix(c(1,3,-2,3,7,1,-2,1,7),3,3,byrow=TRUE)
b=c(-4,4,7)
qr.solve(A,b,tol=1e-7)
solve.qr
```

#### 5.	Set the seed at 4865299. Create a 4x3 matrix M by generating values from uniform (0,1). Solve the system of equations Mx = b, where b = (1,2,3,4) using Gaussian elimination, LU decomposition and QR factorization.


```{r}
set.seed(4865299)
M = matrix(runif(12),nrow=4)
b = c(1,2,3,4)
Solve(M, b)
#Solve by Gaussian Elimination
gaussianElimination(
  M,
  b,
  tol = sqrt(.Machine$double.eps),
  verbose = FALSE
)
#Solve by LU decomposition

#Solve by QR-factorization

QR = qr(M, tol=1e-07)
Q = qr.Q(QR)
R = qr.R(QR)

#(Q)%*%R

qr.solve(M, b, tol=1e-7)
```

