---
title: "Priblem set-1 (DB)"
author: "Srijan Kundu"
date: "2022-08-29"
output: "html_document"
---


## Consider the vectors a = (1, 2, 3, 4, 5, 6) and b = (10, -4, 6, 0, 5, 1). Do the following:

```{r}
a = c(1,2,3,4,5,6)
b = c(10,-4,6,0,5,1)
```
### Lengths of vectors a and b:
```{r}
length(a)
length(b)
```

### Access 4 th element of the vector b:
```{r}
b[4]
```
### Access 2 nd and 5 th element of vector b:
```{r}
b[2]
b[5]
```
### Which elements of b are greater than 2?
```{r}
which(b>2)
```
### Enlist the values of b greater than 2.
```{r}
b[b>2]
```
### Remove the first element of the vector b.
```{r}
c = b[-1]
c
```
### Find maximum and minimum element of b.
```{r}
max(b)
min(b)
```
### Sum of the elements of b.
```{r}
sum(b)
```
### number of elements in b which are less than 3
```{r}
length(b[b<3])
```

### sum of the elements in b that are less than 3
```{r}
sum(b[b<3])
```

### mean of the elements of b
```{r}
mean(b)
```
### median of the elements of b
```{r}
median(b)
```

### range of the elements of b
```{r}
range(b)
```
### variance of the elements of b
```{r}
var(b)
```
### correlation between vectors a and b
```{r}
cor(a,b)
```
### sort the elements of b
```{r}
sort(b)
```

### find the vector containing the minimum, lower quartile, median, upper quartile, and maximum of b
```{r}
summary(b)
```
### vector containing the sum of all of the elements up to that point of b
```{r}
cumsum(b)
```

### vector containing the product of all of the elements up to that point of b
```{r}
cumprod(b)
```
### vector of non-decreasing numbers which are the cumulative maxima of the values in b up to that point
```{r}
cummax(b)
```
### vector of non-increasing numbers which are the cumulative minima of the values in b up to that point
```{r}
cummin(b)
```
### a+b
```{r}
a + b
```
### a-b
```{r}
a-b
```
### a.b
```{r}
a*b
```


## 2. x=(0.9982, 0.9820, 0.2020, 0.6599, 0.9345, 0.1883), y=(0.5182, 0.3012, 0.4167, 0.5364, 0.0787, 0.4995), z=(0.2659, 0.1327, 0.4406, 0.6512, 0.0318, 0.3693).

```{r}
x = c(0.9982,0.9820,0.2020,0.6599,0.9345,0.1883)
y = c(0.5182,0.3012,0.4167,0.5364,0.0787,0.4995)
z = c(0.2659,0.1237,0.4406,0.5412,0.0318,0.3693)
```

### Find parallel minima and maxima using pmin and pmax functions.
```{r}
pmin(x, y, z)
pmax(x, y, z)
```
### Find sum of the three largest values in x.
```{r}
x_1 <- sort(x, decreasing = TRUE)
sum(x_1[1:3])
```

### Find the angle between x and y.
```{r}
theta <- acos( sum(x*y) / ( sqrt(sum(x * x)) * sqrt(sum(y * y)) ) )
angle = theta*180/pi
angle
```

### Euclidean distance between x and y.
```{r}
euclidean_dist <- function(x, y) sqrt(sum((x - y)^2))
euclidean_dist(x, y)
```

### Calculate the dot product between x and y.
```{r}
dot(x, y)
```