---
title: "SC-MD_Nov-21_1"
author: "Srijan Kundu"
date: "2022-11-21"
output: pdf_document
---

```{r}
set.seed(1)
```


## Question 1:
Let $X$ be a random variable such that $X \sim Bin(10, 0.3)$.
Then,

### Question 1(a):
Find:
- $P(X = 5)$
```{r}
dbinom(5, 10, 0.3)
```

- $P(X \leq 1)$
```{r}
pbinom(1, 10, 0.3)
```

- $P(X > 4)$
```{r}
pbinom(4, 10, 0.3, lower.tail = FALSE)
```

- The median of $X$
```{r}
qbinom(0.5, 10, 0.3)
```

### Question 1(b)
Draw a random sample of size 100 from the distribution of $X$ and obtain the proportion of observations which are $\leq 3$.

```{r}
data = rbinom(100, 10, 0.3)
length(data[data <= 3])/100
```
## Question 2:
A car hire company has two cars which it hires out a day. The number of
demands for a car on each day has a Poisson distribution with mean 1.5. Find the proportion of days on which:

### Question 2(a):
Neither car is used: 
```{r}
dpois(0, 1.5)
```
### Question 2(b):
One car remains idle:
```{r}
dpois(1, 1.5)
```
### Question 2(c):
Some demands are refused:
```{r}
ppois(2, 1.5, lower.tail = FALSE)
```

## Question 3: 
A batch of parts contains 100 parts from a local supplier of tubing and 200 parts from a supplier of the neighboring state. If four parts are selected randomly and without replacement

### Question 3(a):
What is the probability that they are all from the local supplier?
```{r}
dhyper(4, 100, 200, 4)
```
### Question 3(b):
What is the probability that two or more parts in the sample are from the
local supplier?
```{r}
phyper(1, 100, 200, 4, lower.tail = FALSE)
```
### Question 3(c):
What is the probability that at least one part in the sample is from the local supplier?
```{r}
1 - phyper(0, 100, 200, 4)
```
## Question 4:
Suppose a fair coin is tossed until the first head appears. Find the probability that:

### Question 4(i):
There will be exactly five tails before the first head appears.
```{r}
dgeom(5, 0.5)
```
### Question 4(ii):
There will be at most 2 tails before the first head.
```{r}
pgeom(2, 0.5)
```
### Question 4(iii):
There will be at least 5 tails before the first head appears.
```{r}
pgeom(4, 0.5, lower.tail = FALSE)
```
### Question 4(iv):
The median number of tails before the first head.
```{r}
qgeom(0.5, 0.5)
```

## Question 5:
When Stephane plays chess against his favorite computer program, he wins with probability 0.60. Assuming independence find the probability that Stephane’s fifth win happens when he plays his eighth game.
```{r}
dnbinom(3, 5, 0.6)
```
*Here, $x \sim NB(5, 0.6)$,where $x$ is the number of failures preceding $r^{th}$ success.*


## Question 6:
The height of students in a large college is found to have a normal distribution with mean 162.50 cm and standard deviation 6 cm. Find the probability that a student selected at random will have:

### Question 6(i):
Height greater than 168 cm:
```{r}
pnorm(168, 162.5, 6, lower.tail = FALSE)
```
### Question 6(ii):
Height less than or equal to 150 cm:
```{r}
pnorm(150, 162.5, 6, lower.tail = TRUE)
```
### Question 6(iii):
Height between 150 and 168 cm
```{r}
pnorm(168, 162.5, 6) - pnorm(150, 162.5, 6)
```

## Question 7:
The marks obtained by candidates in Mathematics (full marks 100) in a certain examination are found to be normally distributed with a certain mean and standard deviation. If 10% of the candidates obtain 60% or more marks, 40% failed to pass (minimum marks for pass is 30), find the mean and standard deviation of the distribution of marks.

```{r}
qnorm(0.4, 0, 1)
qnorm(0.1, 0, 1, lower.tail = FALSE)
```
Here, we need to solve for $\mu\;\&\;\sigma$ where 
$$\frac{30 - \mu}{\sigma} = -0.25,\;\text{and}$$
$$\frac{60 - \mu}{\sigma} = 1.28$$

## Question 8:
It is known that the lifetime t of electron tubes is distributed as exponential with mean m. Find the probability that an electron tube chosen at random survives for more than 400 hours when m=200.
```{r}
pexp(400, 1/200, lower.tail = FALSE)
```
For what value of m is this probability 0.5?
```{r}
qexp(0.5, 1/400)
```


## Question 9:
A daily consumption of milk in a city, in excess of 20000 liters, is approximately distributed as a Gamma with shape parameter 0.0001 and scale parameter 2. The city has a daily stock of 30000 liters. What is the probability that the stock is insufficient on a particular day?
```{r}

```

## Question 10:
The percentage of impurities per batch in a certain chemical product is a random variable X following a beta(3,2) distribution. A batch with more than 40% impurities cannot be sold. What is the probability that a randomly selected batch cannot be sold because of excessive impurities?
```{r}

```

## Question 11:
Suppose the lifetime of a motor has a lognormal distribution with shape parameter 11 hours and scale parameter 1.3 hours. What is the probability that the lifetime exceeds 12,000 hours?
```{r}

```










