---
title: "DB_PS5"
author: "Srijan Kundu"
date: "2022-11-20"
output: pdf_document
---

```{r}
library(matlib)
library(pracma)
```
## Problem 1(i)
```{r}
a1 = matrix(c(5,-4,-1,1),2,2,byrow=T)
b1 = c(-10,2)
plotEqn(a1,b1)
```
### Comment:
There exists unique solution for $(x, y)$.

## Problem 1(ii)
```{r}
a2 = matrix(c(1,-2,3,-6),2,2,byrow=T)
b2 = c(1,3)
plotEqn(a2,b2)
```
### Comment:
The two lines overlap each other; implying all points on these lines are solutions for the set of equations.
```{r}
Solve(a2,b2,verbose = T)
```


## Problem 1(iii)
```{r}
a3 = matrix(c(1,-2,3,-6),2,2,byrow=T)
b3 = c(1,11)
plotEqn(a3,b3)
```
### Comment:
These two lines are parallel to each other, i.e., they will never intersect each other at any time. Hence, there does not exist any solution at all.
```{r}
Solve(a3,b3,verbose = T)
```
## Problem 1(iv)
```{r}
a4 = matrix(c(1,-1,2,2,3,1),3,2,byrow=T)
b4 = c(2,1,6)
plotEqn(a4,b4)
```
### Comment:
This set of equations is not solvable. In this problem, set of any two equations taken at a time among the set of three equations, is solvable with unique solution point, but when all three equations are taken at a time, the set is failing to have any unique solution. This kind of set is called inconsistant.

```{r}
Solve(a4,b4,verbose = T)
```
## Problem 1(v)
```{r}
a5 = matrix(c(13,-4,2,-4,11,-2,2,-2,8),3,3,byrow = T)
b5 = c(1,2,6)
plotEqn3d(a5,b5)
```

### Comment:
There exists a unique solution for the given set of linear equations.
```{r}
Solve(a5, b5, verbose = T)
```
## Problem 1(vi)
```{r}
a6 = matrix(c(1,2,3,2,5,2,6,-3,1),3,3,byrow=T)
b6 = c(6,4,2)
plotEqn3d(a6,b6)
```
### Comment:
There exists a unique solution for the given set of linear equations.
```{r}
Solve(a6, b6, verbose = T)
```
## Problem 2
Let, producer A distributes x1 and x2 many bottles from the production site to distributor C & D respectively. Again, producer B distributes x3 and x4 many bottles to distributor C & D respectively.
According to the problem
x1 + x2 = 475
...(i)
x3 + x4 = 489
...(ii)
x1 + x3 = 542
...(iii)
x2 + x4 = 422
...(iv)

We now solve the following equation as follows:
```{r}
a2 = matrix(c(1,1,0,0,0,0,1,1,1,0,1,0,0,1,0,1),4,4,byrow = T)
a2
```
```{r}
b2 = c(475,489,542,422)
det(a2)
```
Since, det(A) = 0 the given system of linear equations are not solvable.

## Problem 3
Let, the person keeps 100x1 in the bank with annual interest rate 4%, say bank A, and the rest 100x2 in
the other bank with 3% annual rate of interest, say bank B.
100x1 + 100x2 = 15000
x1 + x2 = 150
...(i)
Now, from bank A, he earns an annual interest of $4x1, and from bank B, he earns that of 3x2.
4x1 + 3x2 = 550
...(ii)
We solve the equation (i) & (ii) as follows,
```{r}
a3 = matrix(c(1,4,1,3),2,2)
b3 = c(150,550)
plotEqn(a3,b3,solution = T)
```
```{r}
t(t(solve(a3,b3)))
```
x1 = 100
&
x2 = 50
100x1 = 10000
&
100x2 = 5000

He has invested 10,000 in the bank A with 4% annual rate of interest and 5,000 in bank B with 3% annual
rate of interest.

## Problem 4
```{r}
Sys.setenv(RGL_USE_NULL=TRUE)
```

The given system of equation is:
x1 + 3x2 − 2x3 = −4
3x1 + 7x2 + x3 = 4
−2x1 + x2 + 7x3 = 7

```{r}
a = matrix(c(1,3,-2,3,7,1,-2,1,7),3,3, byrow = T)
paste("coefficient matrix A is:")
a
b = c(-4,4,7)
paste("vector b is:")
b
```

### Solve by Gaussian Elimination
```{r}
gaussianElimination(a,b,verbose = T, tol = (.Machine$double.eps)**0.5)
```
The solution is:
x1 = 3
x2 = −1
x3 = 2

### Solve by LU Decomposition
```{r}
library(matrixcalc)
```

```{r}
lu_a = lu.decomposition(a)
lu_a$L
lu_a$U
```
Ax = b
LUx = b
Now, Ux = y
Ly = b
We first solve y = L−1b
```{r}
y = solve(lu_a$L,b)
y
```
Then we solve, x = U −1y
```{r}
x = solve(lu_a$U,y)
t(t(x))
```
The solution is:
x1 = 3
x2 = −1
x3 = 2

### Solve by QR Factorization
```{r}
qra = qr(a, tol = 1e-7, LAPACK = F)
Ra = qr.R(qra)
Qa = qr.Q(qra)
```
The R matrix is:
```{r}
Ra
```
The Q matrix is:
```{r}
Qa
```

The R−1 matrix is:
```{r}
Ra_inv = inv(Ra)
Ra_inv
```
The QT matrix is:
```{r}
Qa_tran = t(Qa)
Qa_tran
```
The pseudo inverse of the matrix given is:
```{r}
pseudoa = Ra_inv%*%Qa_tran
pseudoa
```
The final solution is:
```{r}
sol = pseudoa%*%b
t(t(sol))
```
### Solve by Cholesky Factorization
```{r}
isposdef(a)
```

Since, A is not a positive definite matrix, hence Cholesky factorization is not applicable.

## Problem 5
```{r}

```

