---
title: "Practical Problem Set - 4 (DB)"
author: "Srijan Kundu"
date: "Nov 05, 2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(matlib)
library(pracma)
```

## Question 1: Let $S$ be the 2‐dimensional subspace of $R^3$ spanned by the orthogonal vectors $v_1 = (1, 2, 1)$ and $v_2 = (1, −1, 1)$. Write the vector $v = (−2, 2, 2)$ as the sum of a vector in $S$ and a vector orthogonal to $S$.

```{r}
v11 = c(1, 2, 1)
v12 = c(1, -1, 1)
v13 = c(-2, 2, 2)
v14 = v11*dot(v13, v11)/dot(v11, v11) + v12*dot(v13, v12)/dot(v12, v12)
v14
v15 = v13 - v14
v15
```
Here, the vector $(-2, 2, 2) = (0, 2, 0) + (-2, 0, 2)$; where $(0, 2, 0) \in S$ and $(-2, 0, 2) \perp S$.

## Question 2: Let $P$ be the subspace of $R^3$ specified by the equation $2 x + y + 2 z = 0$. Find the distance between $P$ and the point $q = (3, 2, 1)$.
```{r}
v21 = c(2, 1, 2)
v22 = c(3, 2, 1)
abs(dot(v21, v22))/Norm(v21)
```
The required distance is 3.33 units.

## Question 3: 	Let $H$ be the 3‐dimensional subspace of $R^4$ with basis $B = \{v_1 = (0,1,-1,0), v_2 = (0,1,0,1), v_3 = (1,-1,0,0)\}$.
```{r}
v31 = c(0, 1, -1, 0)
v32 = c(0, 1, 0, 1)
v33 = c(1, -1, 0, 0)
M31 = cbind(v31, v32, v33)
M31
```

### 3.(i) Find the orthogonal basis for $H$.
```{r}
M32 = GramSchmidt(M31, normalize = F, verbose = F, tol = sqrt(.Machine$double.eps))
M32
```
The columns of the matrix $M_{32}$ above are an orthogonal basis of $H$.

### 3.(ii) Find the orthonormal basis for $H$.
```{r}
M33 =GramSchmidt(M31, normalize = T, verbose = F, tol = sqrt(.Machine$double.eps))
M33
```
The columns of the matrix $M_{33}$ above are an orthonormal basis of $H$.

### 3.(iii) What are the components of the vector $x = (1, 1, -1, 1)$ relative to this orthonormal basis?
```{r}
v33 = c(1, 1, -1, 1)
c31 = dot(v33, M33[, 1])
c32 = dot(v33, M33[, 2])
c33 = dot(v33, M33[, 3])
v34 = c(c31, c32, c33)
v34
```
```{r}
#check if v34 is in H
rref(cbind(M33, v33))
```
As we can see, $v_{33}$ can be spanned by first 3 column vectors of the augmented matrix above.

The components of the vector $x = (1, 1, -1, 1)$ relative to this orthonormal basis represented by the columns of $M_{33}$ are $1.414,\;0.816,\;1.155$ respectively.
```{r}
#verification
v33
t(M33 %*% matrix(v34))
```


### 3.(iv) What happens if you attempt to find the components of the vector $y = (1, 1, 1, 1)$ relative to the orthonormal basis?
```{r}
v35 = c(1, 1, 1, 1)
c35 = dot(v35, M33[, 1])
c36 = dot(v35, M33[, 2])
c37 = dot(v35, M33[, 3])
v36 = c(c35, c36, c37)
v36
```

```{r}
#check if v35 is in H
rref(cbind(M33, v35))
```
As we can see, $v_{35}$ can not be spanned by first 3 column vectors of the augmented matrix above.

```{r}
#verification
v35
t(M33 %*% matrix(v36))
```
As we can see, $v_{35} \neq (0.5, 0.5, 0.5, 1.5)$. This is because the vector $v_{35}$ is not in $H$, meaning no linear combination of basis vectors of $H$ can give $(1, 1, 1, 1)$.


## Question 4: Find the Kronecker product of the following matrices and verify that $A⊗B ≠ B⊗A$:

### 4.(i) $A = \begin{bmatrix}2&3\\0&1 \end{bmatrix}, B = \begin{bmatrix}0&-1\\-1&1 \end{bmatrix}$.
```{r}
M41 = matrix(c(2, 3, 0, 1), nrow = 2, byrow = T)
M42 = matrix(c(0, -1, -1, 1), nrow = 2, byrow = T)
M41%x%M42
M42%x%M41
```

### 4.(ii) $A = \begin{bmatrix}1&2\\3&4\\1&0 \end{bmatrix}, B = \begin{bmatrix}0&5&2\\6&7&3 \end{bmatrix}$.
```{r}
M43 = matrix(c(1, 2, 3, 4, 1, 0), nrow = 3, byrow = T)
M44 = matrix(c(0, 5, 2, 6, 7, 3), nrow = 2, byrow = T)
M43%x%M44
M44%x%M43
```

## Question 5: Let $u = \begin{pmatrix} 1\\0\end{pmatrix}, v = \begin{pmatrix}0\\1 \end{pmatrix}$. Find $u⊗u, u⊗v, v⊗u$ and $v⊗v$. Which space do they span?
```{r}
V51 = c(1, 0)
V52 = c(0, 1)
#u⊗u
matrix(V51)%x%matrix(V51)
#u⊗v
matrix(V51)%x%matrix(V52)
#v⊗u
matrix(V52)%x%matrix(V51)
#v⊗v
matrix(V52)%x%matrix(V52)

```
These 4 vectors together span $R^4$.

## Question 6: Let $A = \begin{pmatrix}2&0&1\\3&1&0 \end{pmatrix}, B = \begin{pmatrix}1&2&2\\1&2&0 \end{pmatrix}$. Find $rank(A), rank(B)$ and $rank(A ⊗ B)$.
```{r}
M61 = matrix(c(2, 0, 1, 3, 1, 0), nrow = 2, byrow = T)
M62 = matrix(c(1, 2, 2, 1, 2, 0), nrow = 2, byrow = T)
#rank(A)
R(M61)
#rank(B)
R(M62)
#rank(A ⊗ B)
R(M61 %x% M62)
```

