---
title: "SC-MD_Sept-19"
author: "Srijan Kundu"
date: "2022-09-19"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(matlib)
```


## Dataframe
A dataframe is a collection of vectors (may be of similar or different nature), but of equal length.

```{r cleaning enviorenment}
rm(list=ls())
```
Define some variables:
```{r}
ht = c(1.53,1.62,1.49,1.68,1.55,1.79,1.64)
wt = c(45,82,42,55,41,72,68)
gn = c("F", "F", "M", "M", "F", "M", "M")
```
Storing the above data in a single data-structure.
```{r}
data = data.frame(ht, wt, gn)
is.data.frame(data)
typeof(data)
```
```{r}
summary(data)
```
Data of any variable can be extracted using the accessor operator, using the `$` sign.
```{r}
data$ht
data$gn
```
To obtain the data on any particular variable for any particular unit, we run `data[unit_number, variable_number]`

```{r}
data[1, ]
data$ht[1]
data[3, 3]
data[, 3]
```
Obtain the data for all persons who satisfy the criteria: wt>65
```{r}
data$wt>65
data[data$wt>65, ]
```
Obtain data for all people who satisfy the criteria weight > 60 and height > 1.64.
```{r}
data[data$wt>60 & data$ht > 1.64, ]
```
```{r}
data[data$wt>60 | data$ht > 1.64, ]
```

Obtain the data for males.
```{r}
data[data$gn == "M", ]
```
Obtain the data on height for people with weight > 65.
```{r}
data[data$wt>65, 1]
```
The function `str` is very useful for finding more about the structure of a dataframe.
```{r}
str(data)
```
```{r}
names(data)
```
Sort the datafame wrt height.
```{r}
order(data$ht)
data[order(data$ht), ]
```
The function `order` takes a vector as input, and returns the vector of indices that sorts out the input order.
Calculate the mean of height from this dataframe.
```{r}
mean(data$ht)
```
To apply a function on each and every variable of a dataframe, we use the function `sapply(data, function)`.
```{r}
sapply(data, mean)
```
```{r}
sapply(data$wt, sum)
```
Take a dataframe with 5 individuals with marks:
Stat: 92, 87, 55, 84, 90
Math: 87, 65, 32, 99, 47
```{r}
stat = c(92, 87, 55, 84, 90)
math = c(87, 65, 32, 99, 47)
data1 = data.frame(stat, math)
data1
```
Obtain mean, variance and sum.
```{r}
sapply(data1, sum)
sapply(data1, var)
sapply(data1, mean)
```

```{r}
summary(data1)
```
## Matrix

```{r}
A = matrix(c(1,4,7,2,5,8,3,6,9), nrow = 3, ncol = 3, byrow = T)
A
```
```{r package-matlib}
echelon(A, verbose = T, frac = T)
```
In matrix, to extract the `(i,j)th` element, we use `A[i][j]`.
```{r}
A[1, 3]
```
```{r}
A[, c(1,3)]
A[, -2]
```
```{r}
A[-2, ]
```
Obtain the mean of the first row.
```{r}
mean(A[1, ])
```
```{r margin_is_1_for_rows,_2_for_columns}
apply(A, 1, mean)
apply(A, 2, mean)
```
`sapply` is to be applied on dataframe; `apply` is to be applied on array.

Storing the matrix in a dataframe:
```{r}
M = data.frame(A)
is.data.frame(M)
is.data.frame(A)
```


```{r}
M = as.matrix(A)
M
```
```{r}
B = matrix(c(2,3,1,3,2,6,7,9,0), nrow = 3, byrow = T)
B
```
Row-augmentation of two matrices can be done by using the function `rbind`, but the columns of the matrics has to be same.
Similarly, column augmentation can be done using the function `cbind`, but the number of rows of the two matrics must be same

```{r}
rbind(A, B)
cbind(A,B)
```
```{r operation_gets_applied_to_all_elements}
A+2
```

```{r element-wise}
A/B
```
Sum of all elements of a matrix:
```{r}
sum(A)
```
Make a new matrix whose (i, j)th element is the sin of the (i,j)th element of A.
```{r}
sin(A)
```
Element wise operation is possible in R.

## Matrix Algebra
Matrix addition
```{r}
A+B
```
Matrix multiplication
```{r}
A%*%B
```
Transpose of a matrix:
```{r}
t(A)
```
Determinant of a matrix:
```{r}
det(B)
```
Inverse of matrix B:
```{r}
solve(B)
```
Eigen values and eigen vecotrs:
```{r}
eigen(B)
#This gives orthonormal eigen vectors
```
Solving a system of linear equations:
```{r}
b = c(1,3,5)
solve(B, b)
```

```{r}
A = matrix(1:4,nrow = 2)
B = c(11, 2, 3)
A+B
```
```{r}
library(pracma)
```
```{r}
R(A)
rank(A)
Rank(A)
```
```{r}
library(Matrix)
rankMatrix(A)
```
## List
```{r}
u = 1:5
v = 1:3
list1 = list(u, v)
list1
```
```{r}
list1[[1]]
list1[[1]][2]
```
```{r}
list2 = list(a = u, b = v)
list2
```
Mean of first list:
```{r}
mean(list2[[1]])
```
```{r}
lapply(list1, mean)
```
```{r}
unlist(list1)
```
Give name to the columns:
```{r}
colnames(A) = c("col1", "col2")
A
rownames(A) = c("row1", "row2")
colnames(A) = month.abb[1:2]
A
```
























